\documentclass[11pt]{article}

\author{August Valera}

\usepackage{fullpage, lmodern, hyperref}
%\usepackage[sfdefault]{roboto} % eventually, but it's hard
\usepackage{geometry} % sets size
\geometry{
  letterpaper,
  margin=1in,
  tmargin=1.5in,
  headsep=0.25in,
  headheight=1in,
}
\usepackage{titlesec} % disables break after section titles
\titlespacing\section{0pt}{\parskip}{-\parskip}
\usepackage{parskip} % disables indentation
\usepackage{enumitem}
\setlist[description]{leftmargin=*} % disables indentation for lists
\setlist[itemize]{leftmargin=*}
\usepackage[none]{hyphenat} % disables splitting words
\usepackage{attachfile} % attaches source code
\usepackage{fancyhdr} % headings and footers
\renewcommand{\footrulewidth}{0.4pt}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{\huge August Valera}
\fancyhead[R]{
  \small
  \url{avalera@ucsc.edu} --- +1 (616) 284-1018 \\
  1010 Pacific Ave. \# 212, Santa Cruz, CA 95060 \\
  \url{http://linkedin.com/in/AugustValera}
}
\fancyfoot[L]{
  \small Compiled \textit{\today} with {\LaTeX}, latest
  \url{http://bitbucket.org/4U6U57/resume/raw/HEAD/cover.pdf?at=cmpe185}
}
\usepackage[yyyymmdd]{datetime} % date for footer in ISO
\renewcommand{\dateseparator}{--}

\begin{document}

\pagenumbering{gobble}

\today

\vspace{12pt}
Facebook \\
1 Hacker Way \\
Menlo Park CA 94025

\vspace{12pt}

RE: Front End Engineer, Intern/Co-op

\vspace{12pt}
Dear Hiring Manager,

\vspace{12pt}
I am writing in regards to the front end engineering internship available at
your Menlo Park headquarters. As a Computer Engineering undergraduate with a
concentration in Computer Systems, I am interested in working with you to
develop and improve your user facing systems. Although I am in engineering,
UI/UX has always been one of my main interests, and I have developed front-end
infrastructure in the context of mobile app development (Android) and web
applications (AngularJS). However, my knowledge on the subject is deep but
limited in scope. I hope to use this internship at Facebook to widen my
knowledge and make some connections with a wider variety of front-end skills
(hopefully, to the same extent that Facebook connects its users across the
globe).

As mentioned previously, I have some experience in front-end as a freelance
developer, both in creating my own interface standards and using preexisting
specifications, such as Google's Material Design. Some projects that I have
worked on was a dining hall menu app
(\url{https://github.com/ChandlerMoeller/TestAppPleaseIgnore}), where I served
as the user interface advisor and one of the interface developers (Android,
Java/XML), as well as a garden monitoring microcontroller, for which I single
handedly built the web application that interfaced with the microcontroller
(\url{https://github.com/SargisYonan/Autonomous_Garden_Project}). In addition, I
also have an extensive background in debugging and QA, from my job as a Teaching
Assistant (Undergraduate) for a multitude of college level Computer Science
courses.

I believe that the skills described above, as well as those listed on my
attached resume qualify me as a strong contender for your internship position. I
look forward to developing for Facebook, and contributing to it's goals of
making the world more open and connected. Please contact me by email or phone if
your have any further questions, and thank your for your consideration.

\vspace{12pt}
Sincerely,

\vspace{24pt}
August Valera

\end{document}
